Towards Accelerating Deep Neural Network Training on FPGAs: Facilitating the Use of Variable Precision\\ \Large{(Unrefereed Workshop Manuscript)}

### 2018-07-04 SWoPP2018 Paper/paper.tex
Removed comment.
Minor change to contribution list.
Final affiliation changes.

\title{Towards Accelerating Deep Neural Network Training on FPGAs: Facilitating the Use of Variable Precision\\ \Large{(Unrefereed Workshop Manuscript)}}
\affiliate{TiTech}{Tokyo Institute of Technology, 
Meguro-ku, Tokyo 152--8550, Japan}
\affiliate{TUDelft}{Delft University of Technology, Mekelweg 2, 2628 CD Delft, Netherlands}
\affiliate{Riken}{RIKEN Center for Computational Science, Chuo-ku, Kobe, Hyogo 650-0047 Japan}
\affiliate{AIST}{National Institute of Advanced Industrial Science and Technology, Chiyoda-ku, Tokyo 100-8921 Japan}

@@

%\begin{keyword}
%Journal of Information Processing, \LaTeX, style files, ``Dos and
% Don'ts'' list
%\end{keyword}

@@

We contribute with the following:
\begin{itemize}
\item Proposed design for a generalized FPGA training architecture targeting variable numerical formats, and
\item Evaluation and analysis of core computation patterns, including FPGA resource utilization
\end{itemize}

>>>>

\title{Towards Accelerating Deep Neural Network Training on FPGAs: Facilitating the Use of Variable Precision\\ \Large{(Unrefereed Workshop Manuscript)}}
\affiliate{TiTech}{Tokyo Institute of Technology, 
Meguro-ku, Tokyo 152--8550, Japan}
\affiliate{TUDelft}{Delft University of Technology, Mekelweg 2, 2628 CD Delft, Netherlands}
\affiliate{Riken}{RIKEN Center for Computational Science, Chuo-ku, Kobe, Hyogo 650-0047 Japan}
\affiliate{AIST}{AIST - Tokyo Tech Real World Big-Data Computation Open Innovation Laboratory, Meguro-ku, Tokyo 152-8550, Japan}{%National Institute of Advanced Industrial Science and Technology, Chiyoda-ku, Tokyo 100-8921 Japan}

@@

@@

In this paper, we contribute with:
%We contribute with the following:
\begin{itemize}
\item Proposed design for a generalized FPGA training architecture targeting variable numerical formats, and
\item Preliminary evaluation and analysis of core computation patterns for inference with respect to performance and resource utilization
\end{itemize}
